\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-18 popl-2019-journal-v/paper.tex
[POPLjv] Remove macros that leaves out details
[POPLjv] Move encoding function remark (address comment)

\renewcommand{\lre}[1][]{\typesetlr{E}^{#1}}
\renewcommand{\lretrusted}[1][]{\lreg[#1]{\trusted}}
\renewcommand{\lrexj}[1][]{\typesetlr{E}^{#1}_{\mathrm{xjmp}}}
\renewcommand{\lrk}[1][]{\typesetlr{K}^{#1}}
\renewcommand{\lrrg}[2][]{\typesetlr{R}^{#1}_{#2}}
\renewcommand{\lrr}[1][\square,\gc]{\lrrg[#1]{}}
\renewcommand{\lrrtrusted}[1][]{\lrrg[#1]{\trusted}}
\renewcommand{\lro}[1][]{\typesetlr{O}^{#1}}
\renewcommand{\lrol}{\lro[\preceq,(\ta,\stkb,\gsigrets,\gsigcloss)]}
\renewcommand{\lror}{\lro[\succeq,(\ta,\stkb,\gsigrets,\gsigcloss)]}
\renewcommand{\lrvg}[2][]{\typesetlr{V}^{#1}_{#2}}
\renewcommand{\lrvtrusted}[1][]{\lrvg[#1]{\trusted}}
\renewcommand{\lrp}{\typesetlr{P}}

\renewcommand{\lrrs}{\typesetlr{R}}
\renewcommand{\lrm}{\typesetlr{M}}
\renewcommand{\lrcomp}[1][]{\typesetlr{C}^{#1}}
\renewcommand{\lrec}[1][]{\typesetlr{EC}^{#1}}
\renewcommand{\lrheap}[1][]{\typesetlr{H}^{#1}}

@@

Finally in the interpretation of $\tisptr{}{}$, the machine uses an encode function for word types $\encType{}$.
This function encodes each kind of word as an integer.
This is very much like the previous functions.
It encodes each kind of word differently and all words of the same kind to the same integer.
In Section~\ref{subsec:overlay-semantics}, we present an overlay semantics which changes the set of words compared to this machine.
\todo[inline]{Dominique: perhaps delay the discussion of encodetype for the overlay semantics to Section~\ref{subsec:overlay-semantics}?}
The overlay semantics also has a type encoding function which must encode the new words, so they correspond to their representation on this machine.
For instance, the encoding of stack-pointer in the overlay semantics should be the same as the encoding of a capability on this machine.
All the new words in the overlay semantics correspond to a word on this machine, and their encodings should match.
\end{jversion}

@@

The main difference between the two semantics, is that the new one satisfies LSE and WBCF by construction: the abstract machine comes with a built-in stack, inactive stack frames are unaddressable and well-bracketed control flow is built-in to the abstract machine.
Important run-time values like return capabilities and stack pointers are represented by special syntactic tokens that interact with the abstract machine's stack, but during execution, there remains a close, structural correspondence to the actual regular capabilities that they represent.
For example, stack capabilities in the overlay semantics correspond directly to linear capabilities in the underlying semantics, and they have authority over the part of memory that the overlay views as the stack.

>>>>

@@

Finally in the interpretation of $\tisptr{}{}$, the machine uses an encode function for word types $\encType{}$.
This function encodes each kind of word as an integer.
This is very much like the previous functions.
It encodes each kind of word differently and all words of the same kind to the same integer.
\end{jversion}

@@

The main difference between the two semantics, is that the new one satisfies LSE and WBCF by construction: the abstract machine comes with a built-in stack, inactive stack frames are unaddressable and well-bracketed control flow is built-in to the abstract machine.
Important run-time values like return capabilities and stack pointers are represented by special syntactic tokens that interact with the abstract machine's stack, but during execution, there remains a close, structural correspondence to the actual regular capabilities that they represent.
For example, stack capabilities in the overlay semantics correspond directly to linear capabilities in the underlying semantics, and they have authority over the part of memory that the overlay views as the stack.
\begin{jversion}
The new run-time values in the overlay semantics affect the definition of the encoding function $\encType{}$.
All the new values correspond to concrete capabilities on the \trgcm{} machine which the encoding function must respect.
For instance, the encoding of a stack pointer in the overlay semantics should be the same as the encoding of a linear capability on the \trgcm{} machine.
\end{jversion}
